---
title: "Case Studies"
subtitle: ""
author: "Introduction to Data Science with R<br/><a href='https://therbootcamp.github.io'>www.therbootcamp.com</a><br/><a href='https://twitter.com/therbootcamp'>@therbootcamp</a>"
date: "October 2018"
output:
  xaringan::moon_reader:
    css: ["default", "baselrbootcamp.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---

layout: true

<div class="my-footer"><span>
<a href="https://therbootcamp.github.io/"><font color="#7E7E7E">Introduction to Data Science with R, October 2018</font></a>
&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;
<a href="https://therbootcamp.github.io/"><font color="#7E7E7E">www.therbootcamp.com</font></a>
</span></div> 

---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
# see: https://github.com/yihui/xaringan
# install.packages("xaringan")
# see: 
# https://github.com/yihui/xaringan/wiki
# https://github.com/gnab/remark/wiki/Markdown
options(width=110)
options(digits = 4)
```

# 2 Case Studies

Work on one or both case studies designed to repeat the central elements of <high>Data I/O</high>, <high>Data Wrangling</high>, <high>Analysing</high>, and <high>Plotting</high><br>

.pull-left45[

## Clinical trial

Analyse a clinical trial comparing the effectiveness of clinical drugs.<br>

```{r, echo = FALSE}
knitr::include_graphics("https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcS_hbV6L48NKZ-eU39RAx0Lb02lb0LC6ftxSQcwOq6Lf0C6m9Fd")
```

[Clinical Trial Case Study](https://therbootcamp.github.io/Intro2DataScience_2018Oct/_sessions/CaseStudies/Clinical_Data_Case_Study.html)

]

.pull-right45[

## Finance

Study the development of key financial markets across the last 20 years<br>

```{r, echo = FALSE, out.width = "70%"}
knitr::include_graphics("https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcSVoAJwqOBeBlDUx1c-NuQ3TpgS86fpMlnbreACyDKYfOZfJ9bd")
```
<br><br><br>
[Finance Case Study](https://therbootcamp.github.io/Intro2DataScience_2018Oct/_sessions/CaseStudies/Financial_Data_Case_Study.html)

]




